Exploring the Validity Range of PLL Analytical Models

### 2025-05-23 CaseStudies/Example3_2_LimitsoftheTheorySoFar/Report/article/article.qmd
Fixing equations (already with error, neither K nor Kphase nor A0 exist).

# Parâmetros iniciais
N = 5
A0 = 1
KVCO = 10e6
I = 1e-3
Kphase = I / (2 * np.pi)
K = A0 * Kphase * KVCO / N
```

@@

# Parâmetros do PLL
C1 = (Kphase * KVCO) / (N * omega_n**2)
C2 = C1 / 10
R1 = (zeta * 4 * np.pi * N * omega_n) / (I * KVCO)
Cs = C1 * C2 / (C1 + C2)
```

@@

# Análise de resposta em frequência
omega_n_meas = np.sqrt(KVCO * Kphase / (N * (C1 + C2)))
f_n_meas = omega_n_meas/2/np.pi
zeta_meas = (C1 * R1 / 2) * np.sqrt(KVCO * Kphase / (N * (C1 + C2)))
t_m_meas=1/(omega_n_meas*math.sqrt(1-zeta_meas**2))*math.atan(math.sqrt(1-zeta_meas**2)/zeta_meas)
theta_e_m_n_meas = math.sin(omega_n_meas*math.sqrt(1-zeta_meas**2)*t_m_meas)/(math.sqrt(1-zeta_meas**2))*math.e**(-zeta_meas*omega_n_meas*t_m_meas)
theta_e_m_meas = 2 * math.pi

omega_bw_meas = omega_n_meas * np.sqrt(1+2*zeta**2+np.sqrt(4*zeta**4+4*zeta**2+2))
f_bw_meas = omega_bw_meas/2/np.pi

step_m_ang_meas=theta_e_m_meas*omega_n_meas/theta_e_m_n_meas
step_m_lin_meas = step_m_ang_meas/2/math.pi

t_s_meas=math.log(0.01*math.sqrt(1-zeta_meas**2), math.e)/(zeta*omega_n_meas)*(-1)
```

>>>>

# Parâmetros iniciais
N = 5
KVCO = 10e6
I = 1e-3
#Kphase = I / (2 * np.pi)
#K = A0 * Kphase * KVCO / N
```

@@

# Parâmetros do PLL
C1 = (I * KVCO) / (2 * np.pi * N * omega_n**2)
C2 = C1 / 10
R1 = (zeta * 4 * np.pi * N * omega_n) / (I * KVCO)
#Cs = C1 * C2 / (C1 + C2)
```

@@

# Análise de resposta em frequência
omega_n_meas = np.sqrt(KVCO * I / (2 * np.pi * N * C1))
f_n_meas = omega_n_meas / (2 * np.pi)

zeta_meas = (R1 / 2) * np.sqrt(KVCO * I * C1 / (2 * np.pi * N))

t_m_meas = 1 / (omega_n_meas * math.sqrt(1 - zeta_meas**2)) * math.atan(math.sqrt(1 - zeta_meas**2) / zeta_meas)

theta_e_m_n_meas = math.sin(omega_n_meas * math.sqrt(1 - zeta_meas**2) * t_m_meas) / \
                   (math.sqrt(1 - zeta_meas**2)) * math.e**(-zeta_meas * omega_n_meas * t_m_meas)

theta_e_m_meas = 2 * math.pi

omega_bw_meas = omega_n_meas * np.sqrt(1 + 2 * zeta_meas**2 + np.sqrt(4 * zeta_meas**4 + 4 * zeta_meas**2 + 2))
f_bw_meas = omega_bw_meas / (2 * np.pi)

step_m_ang_meas = theta_e_m_meas * omega_n_meas / theta_e_m_n_meas
step_m_lin_meas = step_m_ang_meas / (2 * math.pi)

t_s_meas = math.log(0.01 * math.sqrt(1 - zeta_meas**2)) / (zeta_meas * omega_n_meas) * (-1)
